A Topic Model of Climate Change Literature

### 2017-05-24 main.tex
Update on Overleaf.

@@

>>>>

\begin{figure}
	\includegraphics[width=\linewidth]{plots/ipcc_topics}
    \caption{IPCC references by topic. The bars show the percentage of each topic that has been matched to an IPCC reference}
\end{figure}

@@

\begin{table}
\small
\setlength\tabcolsep{0.1cm}
\begin{tabular}{cccccc}
AR1 & AR2 & AR3 & AR4 & AR5 & AR6 \\
\midrule \\
\input{tables/bottomAR1} & \input{tables/bottomAR2}  & \input{tables/bottomAR3}
 & \input{tables/bottomAR4}  & \input{tables/bottomAR5}  & \input{tables/bottomAR6}
\end{tabular}
\caption{The bottom 5 topics in each assessment period by percentage growth since the last assessment period}
\end{table}
